---
title: "Full Data Compile"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(jsonlite) #we use this package to parse the JSON columns
library(kableExtra)

data_SOL <- read_csv("In/Solitaired/researchstudy-9-5-24-12-32 PM.csv")
data_TMB <- read_csv("In/TMB/solitairecog_data_20240904185255.csv")
  
```

# Introduction


# Formatting and Merging Data

```{r, message = FALSE, results='hide'}

#read in the list of games of the day
gotdSeeds <- read_csv("warmed-up-gotd.csv") 

#Expand JSON columns in Solitaired dataset
data_SOL_parsed <- data_SOL %>% 
  bind_cols(stream_in(textConnection(gsub("\\n", "", data_SOL$data)))) %>% 
  bind_cols(.$user) %>% #user is saved as a dataframe within the dataframe, so we just unlist it
  bind_cols(.$questionnaireData) %>% #same for the questionaire data
  select(-c(data, user, questionnaireData)) %>%  #remove the columns that we no longer need
  left_join(gotdSeeds, by = "seed") %>% 
  rename_with(~ paste0(., "_SOL")) #adding a suffix to the end of each column name to make differentiating variables easier after merging

#Expand JSON columns in TMB dataset
data_TMB_parsed <- data_TMB %>% 
  bind_cols(stream_in(textConnection(gsub("\\n", "", data_TMB$test_params))),
            stream_in(textConnection(gsub("\\n", "", data_TMB$device_scan))),
            stream_in(textConnection(gsub("\\n", "", data_TMB$outcomes))),
            stream_in(textConnection(gsub("\\n", "", data_TMB$URL_params)))) %>% 
  select(-c(test_params,device_scan,outcomes,URL_params)) %>% 
  rename_with(~ paste0(., "_TMB")) %>% #same idea, add a suffix for ease of interpretation
  mutate(tmbUserId_SOL = user_id_TMB) #changing the name of this ID variable for merging

#merging Solitaired and TMB datasets based on the "tmbUserID" column
#here I am using a left merge, so that we only end up with participants who took the TMB tests
merged_SOL_TMB <- data_TMB_parsed %>% left_join(data_SOL_parsed, by = "tmbUserId_SOL") %>% filter(!is.na(game_id_SOL))

#writing the combined dataset, saved with the most recent TMB date
write.csv(merged_SOL_TMB, paste0("Out/fullData_", date, ".csv"))


```

# Checking number of total cases

```{r}

nCases <- nrow(merged_SOL_TMB)

```

There were `r nCases` TMB tests taken. They took place at the following times:

```{r}

merged_SOL_TMB %>% mutate(Hour = format(as.POSIXct(merged_SOL_TMB$statsCreatedAt_SOL, format="%m/%d/%Y %H:%M", tz="UTC"), "%H")) %>% group_by(Hour) %>% summarize(Frequency = n(), Proportion = round(n()/nCases,2)) %>% kable() %>% kable_styling()

```

# What were the statuses of the Solitaired tests?

```{r}

data_SOL_parsed %>% filter(status_SOL != "geo") %>%  group_by(status_SOL) %>% summarize(N = n(), Prop = round(n()/nrow(filter(data_SOL_parsed,status_SOL != "geo")),2)) %>% kable() %>% kable_styling()

```

# How many of the users were unregistered?

```{r}

kable(table(merged_SOL_TMB$newRegistrationUser_SOL)) %>% kable_styling()

```

This makes up `r round(sum(merged_SOL_TMB$newRegistrationUser_SOL,na.rm=TRUE)/nrow(merged_SOL_TMB) * 100,2)`% of the daily cases.

# Distribution of TMB tests

```{r}

merged_SOL_TMB %>% group_by(test_name_TMB) %>% summarize(Frequency = n(), 'Mean Duration' = mean(duration...17_TMB), Proportion = round(n()/nCases,2)) %>% kable() %>% kable_styling()

```

# Distribution of TMB test lengths

```{r}

ggplot(merged_SOL_TMB, aes(x=duration...17_TMB, fill=test_name_TMB)) +
  geom_density(alpha=.25)

```

# Expected variability in items response, in game data

```{r}

ggplot(merged_SOL_TMB, aes(x = completion_time_SOL)) + geom_boxplot() + coord_flip() + ggtitle("Range of Completion Times")
ggplot(merged_SOL_TMB, aes(x = undoCount_SOL)) + geom_boxplot() + coord_flip() + ggtitle("Range of Undo Counts")
ggplot(merged_SOL_TMB, aes(x = hintCount_SOL)) + geom_boxplot() + coord_flip() + ggtitle("Range of Hint Counts")
ggplot(merged_SOL_TMB, aes(x = hkMoveCount_SOL)) + geom_boxplot() + coord_flip() + ggtitle("Range of Hotkey Move Counts")
ggplot(merged_SOL_TMB, aes(x = autoMoveCount_SOL)) + geom_boxplot() + coord_flip() + ggtitle("Range of Auto Move Counts")

```

# Variability in survey data 

```{r}

kable(table(merged_SOL_TMB$age_SOL),col.names = c("Age", "Freq.")) %>% kable_styling()
kable(table(merged_SOL_TMB$gender_SOL),col.names = c("Gender", "Freq.")) %>% kable_styling()
kable(table(merged_SOL_TMB$cognitiveImpairment_SOL),col.names = c("Cognitive Impairment", "Freq.")) %>% kable_styling()

```



