---
title: "Daily Check Code"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
params:
  dateOfInterest: "default"
  data_SOL: "default"
  data_TMB: "default"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(jsonlite) #we use this package to parse the JSON columns
library(kableExtra)

dateOfInterest <- params$dateOfInterest
data_SOL <- params$data_SOL
data_TMB <- params$data_TMB

```

# Introduction

This is the data checked for `r dateOfInterest`.

# Formatting and Merging Data

```{r, message = FALSE, results='hide'}

#read in the list of games of the day
gotdSeeds <- read_csv("warmed-up-gotd.csv") %>% mutate(game_date = as.Date(game_date, "%m/%d/%Y"))
currentGameSeed <- filter(gotdSeeds, game_date == dateOfInterest) %>% pull(seed)

#Expand JSON columns in Solitaired dataset
data_SOL_parsed <- data_SOL %>% 
  bind_cols(stream_in(textConnection(gsub("\\n", "", data_SOL$data)))) %>% 
  bind_cols(.$user) %>% #user is saved as a dataframe within the dataframe, so we just unlist it
  bind_cols(.$questionnaireData) %>% #same for the questionaire data
  select(-c(data, user, questionnaireData)) %>%  #remove the columns that we no longer need
  rename_with(~ paste0(., "_SOL")) #adding a suffix to the end of each column name to make differentiating variables easier after merging

data_SOL_parsed_comparison <- data_SOL_parsed %>% filter(seed_SOL == currentGameSeed) #use this when making the side by side boxplots to compare game data - when grouping, group by "status_SOL" geo = wasn't invited, completed "completed", declined "declined"

#Expand JSON columns in TMB dataset
data_TMB_parsed <- data_TMB %>% 
  bind_cols(stream_in(textConnection(gsub("\\n", "", data_TMB$test_params))),
            stream_in(textConnection(gsub("\\n", "", data_TMB$device_scan))),
            stream_in(textConnection(gsub("\\n", "", data_TMB$outcomes))),
            stream_in(textConnection(gsub("\\n", "", data_TMB$URL_params)))) %>% 
  select(-c(test_params,device_scan,outcomes,URL_params)) %>% 
  rename_with(~ paste0(., "_TMB")) %>% #same idea, add a suffix for ease of interpretation
  mutate(tmbUserId_SOL = user_id_TMB) #changing the name of this ID variable for merging

#as a note here, the "data" column in the TMB dataset is a list of lists,
#and it's all metadata for each individual click within the TMB test. This
#is outside the scope of our project, so I have left it as a JSON column.

#merging Solitaired and TMB datasets based on the "tmbUserID" column
#here I am using a left merge, so that we only end up with participants who took the TMB tests
merged_SOL_TMB <- data_TMB_parsed %>% left_join(data_SOL_parsed, by = "tmbUserId_SOL") %>% filter(seed_SOL == currentGameSeed)

#writing the combined dataset, saved with the most recent TMB date
write.csv(merged_SOL_TMB, paste("out/",dateOfInterest,"merged_Solitaired_TMB.csv",sep="_"))

```

#  Check uniqueness in userID

```{r}

nRepeats <- sum(table(merged_SOL_TMB$tmbUserId_SOL) > 1)

previousRepeats <- sum(data_SOL_parsed$tmbUserId_SOL %in% merged_SOL_TMB$tmbUserId_SOL & data_SOL_parsed$seed_SOL != currentGameSeed)

merged_SOL_TMB_2 <- merged_SOL_TMB %>% distinct(tmbUserId_SOL, .keep_all = TRUE) 

```

There are `r nRepeats` repeated user IDs in today's data. Looking back to previous days, `r previousRepeats` people in the current day participated in previous days. Ideally both these numbers are 0! If instances of people appear more than once in the same day, we have kept the first of those instances for future analyses.


# Checking number of daily cases

```{r}

nCases <- nrow(merged_SOL_TMB_2)

```

On `r dateOfInterest`, there were `r nCases` TMB tests taken. Of those cases, they took place at the following times:

```{r}

merged_SOL_TMB_2 %>% mutate(Hour = format(as.POSIXct(merged_SOL_TMB_2$statsCreatedAt_SOL, format="%m/%d/%Y %H:%M", tz="UTC"), "%H")) %>% group_by(Hour) %>% summarize(Frequency = n(), Proportion = round(n()/nCases,2)) %>% kable() %>% kable_styling()

```

# Checking number of declined/tmb_start/invited cases

The N for completed should be equal to `r nCases`.

```{r}

data_SOL_parsed_comparison %>% filter(status_SOL != "geo") %>%  group_by(status_SOL) %>% summarize(N = n(), Prop = round(n()/nrow(filter(data_SOL_parsed_comparison,status_SOL != "geo")),2)) %>% kable() %>% kable_styling()

```

# How many of the users were unregistered?

```{r}

kable(table(merged_SOL_TMB$newRegistrationUser_SOL)) %>% kable_styling()

```

This makes up `r round(100*sum(merged_SOL_TMB$newRegistrationUser_SOL,na.rm=TRUE)/nrow(merged_SOL_TMB),2)`% of the daily cases.

# Distribution of TMB tests

```{r}

merged_SOL_TMB_2 %>% group_by(test_name_TMB) %>% summarize(Frequency = n(), 'Mean Length' = mean(duration...17_TMB),  Proportion = round(n()/nCases,2)) %>% kable() %>% kable_styling()

```

# Distribution of TMB test lengths

```{r}

ggplot(merged_SOL_TMB_2, aes(x=duration...17_TMB, fill=test_name_TMB)) +
  geom_density(alpha=.25)

```

# Expected variability in items response, in game data

```{r}

ggplot(merged_SOL_TMB_2, aes(x = completion_time_SOL)) + geom_boxplot() + coord_flip() + ggtitle("Range of Completion Times")
ggplot(merged_SOL_TMB_2, aes(x = undoCount_SOL)) + geom_boxplot() + coord_flip() + ggtitle("Range of Undo Counts")
ggplot(merged_SOL_TMB_2, aes(x = hintCount_SOL)) + geom_boxplot() + coord_flip() + ggtitle("Range of Hint Counts")
ggplot(merged_SOL_TMB_2, aes(x = hkMoveCount_SOL)) + geom_boxplot() + coord_flip() + ggtitle("Range of Hotkey Move Counts")
ggplot(merged_SOL_TMB_2, aes(x = autoMoveCount_SOL)) + geom_boxplot() + coord_flip() + ggtitle("Range of Auto Move Counts")

```

# Variability in survey data 

```{r}

kable(table(merged_SOL_TMB_2$age_SOL),col.names = c("Age", "Freq.")) %>% kable_styling()
kable(table(merged_SOL_TMB_2$gender_SOL),col.names = c("Gender", "Freq.")) %>% kable_styling()
kable(table(merged_SOL_TMB_2$cognitiveImpairment_SOL),col.names = c("Cognitive Impairment", "Freq.")) %>% kable_styling()

```



